Summer 2025 ToDo

### 2025-11-05 Relations/Paper/Introduction.tex
Macro update, related works added to intro, main bibliography update.

\subsection{Contributions}
Our contributions are as follows.
\begin{itemize}
  \item Formalization of elementary ARS theory as presented in
  \cite{Terese}, including relevant background;
  % Chapter 1 of
  \item An ontology of termination and confluence properties, and a detailed analysis of logical relationships between them;
  \item Definitions of new ARS concepts that refine our understanding of these relationships;
  \item Marginal improvements to classical confluence and termination criteria;
  \item An examination of several distinct notions of well-foundedness
  in the constructive setting.
\end{itemize}

>>>>

\subsection{Contributions}
Our contributions are as follows.
\begin{enumerate} \label{list:ourContributions}
  \item Formalization of elementary ARS theory as presented in
  \cite{Terese}, including relevant background; \sacomment{Should we remove this contribution as it is provided already in the agda standard library?}
  % Chapter 1 of
  \item An ontology of termination and confluence properties, and a detailed analysis of logical relationships between them;
  \item Definitions of new ARS concepts that refine our understanding of these relationships;
  \item Marginal improvements to classical confluence and termination criteria;
  \item An examination of several distinct notions of well-foundedness
  in the constructive setting.
\end{enumerate}

\subsection{Related works}
% We should cover the following in this section:
% \begin{itemize}
%   \item The IsaFoR/CeTA tool for certification of termination/confluence proofs provided by some automated tool (http://cl-informatik.uibk.ac.at/software/ceta/#introduction). Specifically this paper (https://www.isa-afp.org/entries/Abstract-Rewriting.html) deals with the formalization of strong normalization and Neman's lemma as part of the CeTA project. They use Isabelle for their formalization. 
%   \item This termination portal which gives an overview of various termination tools: https://termination-portal.org/wiki/Termination_Portal. Specifically here is a list of different termination tools: https://termination-portal.org/wiki/Category:Tools . We should talk about what distinguishes our project from a termination tool. 
%   \item Similarly this project is a collection of formalizations of theorems related to term rewrite systems in the language of the proof assistant PVS. http://trs.cic.unb.br/ (here is the formalization of Newman's lemma if you're interested! https://github.com/nasa/pvslib/blob/master/TRS/newman_yokouchi.pvs). 
%   \item Can nention that the agda standard library has a rewriting formalization too based on TeReSe
% \end{itemize}
Several formalizations of elementary ARS theory exist, including projects in Isabelle \cite{isabelleFormalization}, PVS \cite{trs}, and Coq \cite{coqARS}, as well as the Agda standard library \cite{AgdaLibraryRewriting}. Our work distinguishes itself through contributions 2-5 above: the detailed ontology of termination and confluence properties, new ARS concepts, refinements to classical criteria, and  examining multiple notions of well-foundedness.

### 2025-11-05 Relations/Paper/Main.tex
Macro update, related works added to intro, main bibliography update.

>>>>

    \bibitem{AgdaLibraryRewriting}
    Agda Standard Library: Rewriting 
    \newblock{https://agda.github.io/agda-stdlib/v1.7.3/Relation.Binary.Rewriting.html}
    \newblock{Accessed: 5th November 2025}

    \bibitem{isabelleFormalization}
    Christian Sternagel and René Thiemann
    \newblock{https://www.isa-afp.org/entries/Abstract-Rewriting.html}
    \newblock{Accessed: 5th November 2025}

    \bibitem{trs}
    André Galdino, Mauricio Ayala-Rincón
    \newblock{http://trs.cic.unb.br/}
    \newblock{Accessed: 5th November 2025}

    \bibitem{coqARS}

    BLANQUI, FRÉDÉRIC, and ADAM KOPROWSKI. 
    \newblock{“CoLoR: A Coq Library on Well-Founded Rewrite Relations and Its Application to the Automated Verification of Termination Certificates.”}
    \newblock{Mathematical Structures in Computer Science 21, no. 4 (2011): 827–59.}
    \newblock{https://doi.org/10.1017/S0960129511000120.}

### 2025-11-05 Relations/Paper/Summer_2025_TODO.tex
todo update
Macro update, related works added to intro, main bibliography update.

\section*{October 15th TODO / Oct 22nd}
\begin{todolist}     
  \item It's possible to have a term rewrite system with good properties like FB and the relation being decidable. But not satisfying accCor. That is something that can be added in a final touch of the paper. Either a remark or example, where a term rewrite system does not validate accCor. (In the lambda calculus, there are computable perpetual strategies. We think they're concerned with weak normalization. Not sure if it can be done with strong normalization.)
  \item Do a final read through of the information below the figure. Have we captured all the most important information / Are we repeating ourselves?
  \item [\done] Do we want to keep anything in the old/delete section of WF?
  \item Do we want to add anything about counter examples or positive examples? 
  \item [\done] We may want to use words rather than macros in certain locations
  \item [\done] Check through the comments in general in the section. 
  \item (Long term) Investigate: what we've done for natural numbers could be done for an arbitrary ARS (in the counter examples files). The sentence: ''The restriction to $\lnot\lnot$-closed subsets implies (and is equivalent to) 
every subset $P$ being merely \emph{weakly} decidable (satisfying $\lnot \lnot P(x) \lor \lnot P(X)$ 
for all $x$)'' needs further exploration. We could not say it/say it differently. 
\item [\done]  CHange WFseq not not to WFseq- in the macro. We are sticking with this for now. If we have time we can investigate the relation between the two.
\item [\done]  Make the diagram horizontal rather than vertical. Spoof it up and we can compare next week.
\item [\done]  Use of macros in WF section. Double check the right one is being used. Don't use the "is'' macro at all in this section. Be consistent on whether we are using macros. 
\item Does WFseq- with MP== imply WFseq? (W're thinking it will need rdec as well to give us the implication).
\item [\done] make the WF macro bold font?
\item add wfseq not not to the definitions?
\item [\done] Go through the bibliography links. Not all of them are currently working!
\item We want to start looking at examples. What we want to know is whether a first order rewrite system with some minimal properties implies some of our classical properties. E.g. lambda calculus satisfies some of our classical properties. As does first order term rewrite system. Follow up question: how big of an issue is it that accCor is not provable? Can we prove is isn't satisfied? 
\item [\done] Make a connection in the final WF section talking about how SN doesn't imply WN constructively. (we've started writing this sentence). 
\item We may need to add to the WFCounters file, if we have SN implies WN then every subset of the natural numbers is decidable.  
\end{todolist}

>>>>

\section*{October 15th TODO / Oct 22nd}
\begin{todolist}     
  \item It's possible to have a term rewrite system with good properties like FB and the relation being decidable. But not satisfying accCor. That is something that can be added in a final touch of the paper. Either a remark or example, where a term rewrite system does not validate accCor. (In the lambda calculus, there are computable perpetual strategies. We think they're concerned with weak normalization. Not sure if it can be done with strong normalization.)
  \item Do a final read through of the information below the figure. Have we captured all the most important information / Are we repeating ourselves?
  \item [\done] Do we want to keep anything in the old/delete section of WF?
  \item Do we want to add anything about counter examples or positive examples? 
  \item [\done] We may want to use words rather than macros in certain locations
  \item [\done] Check through the comments in general in the section. 
  \item (Long term) Investigate: what we've done for natural numbers could be done for an arbitrary ARS (in the counter examples files). The sentence: ''The restriction to $\lnot\lnot$-closed subsets implies (and is equivalent to) 
every subset $P$ being merely \emph{weakly} decidable (satisfying $\lnot \lnot P(x) \lor \lnot P(X)$ 
for all $x$)'' needs further exploration. We could not say it/say it differently. 
\item [\done]  CHange WFseq not not to WFseq- in the macro. We are sticking with this for now. If we have time we can investigate the relation between the two.
\item [\done]  Make the diagram horizontal rather than vertical. Spoof it up and we can compare next week.
\item [\done]  Use of macros in WF section. Double check the right one is being used. Don't use the "is'' macro at all in this section. Be consistent on whether we are using macros. 
\item Does WFseq- with MP== imply WFseq? (W're thinking it will need rdec as well to give us the implication).
\item [\done] make the WF macro bold font?
\item add wfseq not not to the definitions?
\item [\done] Go through the bibliography links. Not all of them are currently working!
\item We want to start looking at examples. What we want to know is whether a first order rewrite system with some minimal properties implies some of our classical properties. E.g. lambda calculus satisfies some of our classical properties. As does first order term rewrite system. Follow up question: how big of an issue is it that accCor is not provable? Can we prove is isn't satisfied? 
\item [\done] Make a connection in the final WF section talking about how SN doesn't imply WN constructively. (we've started writing this sentence). 
\item We may need to add to the WFCounters file, if we have SN implies WN then every subset of the natural numbers is decidable.  
\item Make sure we have a proof of the implication from SN to WN given FB and decidability of a relation (to back up our claim in our introduction).
\item check TERESE and see first order term rewrite systems example which could be valid for showing classical and constructive formalization coincide. First order term rewrite systems are (always?) fb and R is dec. 
\item [\done] Change the macro for FB so that it is also boldface
\item from wellfounded extra move the implication of fb -> isdec -> isMinDec. move to implications. 
Use this to take this SNdec→WN to have a full proof from fb, isdec, sn -> wn. (issue in moving to fb file due to reversal of relation direction!)
\end{todolist}
